Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-03-20 docs/00-manuscripts/ieee/ieee-manuscript.tex
update xgboost param set

% parameter limits
\begin{table}[h!]
	\centering
	\caption[t]{Hyperparameter ranges and types for each model.
		Hyperparameter notations from the respective R packages were used.}
	\begingroup\scriptsize
	\begin{tabularx}{.5\textwidth}{llXXrXX}
		\\
		\specialcell{Model                                              \\ (package)}                & Hyperparameter              & Type    & Start     & End      & Default \\
		\toprule
		\multirow{3}{*}{\specialcell{RF                                 \\ (ranger)}}       & \texttt{$x_{try}$}    & dbl & 0         & 0.5      & -       \\
		 & \texttt{min.node.size}      & int & 1        & 10      & 1   \\
		 & \texttt{sample.fraction}    & dbl & 0.2      & 0.9     & 1   \\
		\midrule
		\multirow{2}{*}{\specialcell{SVM                                \\ (kernlab)}}     & \texttt{C}                  & dbl & $2^{-10}$ & $2^{10}$ & 1       \\
		 & \texttt{$\sigma$}           & dbl & $2^{-5}$ & $2^{5}$ & 1   \\
		\midrule
		\multirow{7}{*}{\specialcell{XGBoost                            \\ (xgboost)}} & \texttt{nrounds}            & int & 10        & 600      & -       \\
		 & \texttt{colsample\_bytree}  & dbl & 0.3      & 0.7     & 1   \\
		 & \texttt{subsample}          & dbl & 0.25     & 1       & 1   \\
		 & \texttt{max\_depth}         & int & 1        & 10      & 6   \\
		 & \texttt{gamma}              & int & 0        & 10      & 0   \\
		 & \texttt{eta}                & dbl & 0.01     & 0.6     & 0.3 \\
		 & \texttt{min\_child\_weight} & int & 0        & 20      & 1   \\
		\bottomrule
	\end{tabularx}
	\endgroup
	\label{tab:hyperparameter_limits}
\end{table}

>>>>

% parameter limits
\begin{table}[h!]
	\centering
	\caption[t]{Hyperparameter ranges and types for each model.
		Hyperparameter notations from the respective R packages were used.}
	\begingroup\scriptsize
	\begin{tabularx}{.5\textwidth}{llXXrXX}
		\\
		\specialcell{Model                                              \\ (package)}                & Hyperparameter              & Type    & Start     & End      & Default \\
		\toprule
		\multirow{3}{*}{\specialcell{RF                                 \\ (ranger)}}       & \texttt{$x_{try}$}    & dbl & 0         & 0.5      & -       \\
		 & \texttt{min.node.size}      & int & 1        & 10      & 1   \\
		 & \texttt{sample.fraction}    & dbl & 0.2      & 0.9     & 1   \\
		\midrule
		\multirow{2}{*}{\specialcell{SVM                                \\ (kernlab)}}     & \texttt{C}                  & dbl & $2^{-10}$ & $2^{10}$ & 1       \\
		 & \texttt{$\sigma$}           & dbl & $2^{-5}$ & $2^{5}$ & 1   \\
		\midrule
		\multirow{7}{*}{\specialcell{XGBoost                            \\ (xgboost)}} & \texttt{nrounds}            & int & 10        & 70      & -       \\
		 & \texttt{colsample\_bytree}  & dbl & 0.6      & 1       & 1   \\
		 & \texttt{subsample}          & dbl & 0.6      & 1       & 1   \\
		 & \texttt{max\_depth}         & int & 3        & 15      & 6   \\
		 & \texttt{gamma}              & int & 0.05     & 10      & 0   \\
		 & \texttt{eta}                & dbl & 0.1      & 1       & 0.3 \\
		 & \texttt{min\_child\_weight} & int & 1        & 7       & 1   \\
		\bottomrule
	\end{tabularx}
	\endgroup
	\label{tab:hyperparameter_limits}
\end{table}
